04-1 - Refitted models

### 2023-01-26 scripts/r/04-1_refitted.Rmd
filter out GAMM from divergent transition calculation

# Load all models, find those with DTs and get min/max, store in tibble
divergent_transitions <- 
  dir_ls(path = here("data/analyses/models"), regexp = ".rds$") %>% 
  as_tibble() %>% 
  transmute(
    path = value,
    mod_name = str_remove(path, here("data/analyses/models/")), 
    mod_name = str_remove(mod_name, ".rds"), 
    model = map(path, ~ readRDS(file = .))
  ) %>% 
  mutate(
    nuts = map(model, nuts_params), 
    dts = map(nuts, get_dts)) %>% 
  unnest(dts) %>% 
  select(mod_name, dts) %>% 
  filter(dts != 0) %>% 
  summarize(n = nrow(.), min_dt = min(dts), max_dt = max(dts))

>>>>

# Load all models, find those with DTs and get min/max, store in tibble
divergent_transitions <- 
  dir_ls(path = here("data/analyses/models"), regexp = ".rds$") %>% 
  as_tibble() %>% 
  transmute(
    path = value,
    mod_name = str_remove(path, here("data/analyses/models/")), 
    mod_name = str_remove(mod_name, ".rds"), 
    model = map(path, ~ readRDS(file = .))
  ) %>% 
  filter(mod_name != "petauroides_fistulator_1_f0_cat") %>% 
  mutate(
    nuts = map(model, nuts_params), 
    dts = map(nuts, get_dts)) %>% 
  unnest(dts) %>% 
  select(mod_name, dts) %>% 
  filter(dts != 0) %>% 
  summarize(n = nrow(.), min_dt = min(dts), max_dt = max(dts))
